Visual Analysis of Ligand Trajectories in Molecular Dynamics

### 2018-09-14 paper.tex
Started overview

%% \section{Introduction} %for journal use above \firstsection{..} instead
TODO

@@

@@

@@

\section{Discussion (+ Future Work)}

>>>>

%% \section{Introduction} %for journal use above \firstsection{..} instead
\begin{itemize}
  \item Motivation
  \item Ligand binding (Method + Trajectory data)
  \item Contribution
\end{itemize}

@@

\begin{itemize}
  \item Trajectories visualization
  \item Differences -- ligand MD trajectory, waters
  \item Missing?
\end{itemize}

@@

\subsection{Ligand Binding Trajectories}

TODO Jak moc se budeme rozepisovat? ENDTODO
When designing the proposed visualization system, we used ligand trajectories data that was computed using our own approach to the ligand binding simulation.
Our simulation method is inspired by robotics, and it exploits a motion planning algorithm~\cite{lavalle2006planning} in order to navigate the ligand through the void space of a molecule.
Specifically, we implemented a modification of the Rapidly-exploring random tree (RRT)~\cite{lavalle1998rapidly} algorithm.
We modified the original algorithm such that it does not sample the void space uniformly.
Instead, we first compute the Voronoi diagram which represents the void space whithin a molecule.
In order to do this, we represent the molecule using van der Waals spheres of its atoms and we compute the aditively weighted Voronoi diagram of atom spheres.
Then, we employ the Voronoi diagram during the sample generation phase of the RRT algorithm such that we bias the sample position towards the Voronoi vertices [VCBM2018? or else?].
Our modification is based on the assumption that it is more probable to find a ligand transport path near the largest voids within a molecule.
This assumption is also utilized by the state-of-the-art molecular tunnel detection algorithms~\cite{yaffe2008molaxis, chovancova2012caver, sehnal2013mole}.
Although we implemented our own ligand binding simulation algorithm, the proposed visualization system is not restricted to it.
On the contrary, we designed the visualization with other ligand binding simulation tools in mind (see Section~\ref{sec:discussion}).

TODO Autodock Vina?

TODO describe visualization input data
TODO describe direct 3D visualization?

@@

\section{Discussion (+ Future Work)}
\label{sec:discussion}
